---
title: "P8105 Homework 1"
author: Yushan Wang
output: github_document
---

```{r, echo = FALSE, message=FALSE}
library(tidyverse)
```

## Probelm 1

This code chunk creates a data frame consists of numeric, logical, character and factor vectors.

```{r}
set.seed(12)

df <- tibble(
  x = rnorm(10),
  y = x > 0,
  z = c("red", "red", "red", "red", 
        "blue", "blue", "blue", 
        "yellow", "yellow", "yellow"),
  w = factor(z)
)
```

Try to take the mean of each variable in the dataframe

```{r}
mean(pull(df,x))
mean(pull(df,y))
mean(pull(df,z))
mean(pull(df,w))
```

I can take the mean of variables x and y , which are numeric and logical vectors.

I can not take the mean of variables z and w, because they are character and factor vectors.


Below is the code chunk that applies as.numeric function to the logical, character, and factor variables. No output will be shown

```{r, results = 'hide', warning = FALSE}
as.numeric(pull(df,y))
as.numeric(pull(df,z))
as.numeric(pull(df,w))
```


