---
title: "P8105 Homework 1"
author: Yushan Wang
output: github_document
---

```{r, echo = FALSE, message=FALSE}
library(tidyverse)
library(ggplot2)
```

## Probelm 1

**This code chunk creates a data frame consists of numeric, logical, character and factor vectors.**

```{r}
set.seed(12)

df <- tibble(
  x = rnorm(10),
  y = x > 0,
  z = c("red", "red", "red", "red", 
        "blue", "blue", "blue", 
        "yellow", "yellow", "yellow"),
  w = factor(z)
)
```

**Try to take the mean of each variable in the dataframe**

```{r}
mean(pull(df,x))
mean(pull(df,y))
mean(pull(df,z))
mean(pull(df,w))
```

I can take the mean of variables x and y , which are numeric and logical vectors.
I can not take the mean of variables z and w, because they are character and factor vectors.


**Below is the code chunk that applies as.numeric function to the logical, character, and factor variables. Output will not be shown**

```{r, results = 'hide', warning = FALSE}
as.numeric(pull(df,y))
as.numeric(pull(df,z))
as.numeric(pull(df,w))
```

Logical and factor vectors are successfully converted to numeric vectors.
Character vector can not be converted to numeric vector.

The failure of taking mean in the above section is because only numeric and logical vectors can take means. For logical vector, 1 represents True and 0 represents False.

## Problem 2

**Loading the penguins dataset**

```{r}
library(palmerpenguins)
data("penguins", package = "palmerpenguins")
```

**Descriptions of the penguins dataset**

The variable names in this dataset are: 
`r names(penguins)`.

The table below shows the number of each species in the *species* variable

```{r, echo=FALSE}
summary(pull(penguins,species))
```

The table below shows the number of each island type in the *island* variable

```{r, echo=FALSE}
summary(pull(penguins,island))
```

The table below shows the min, 1st quartile, median, mean, 3rd quartile, max value, and number of NA's of the variable *bill_length_mm* 

```{r, echo=FALSE}
summary(pull(penguins,bill_length_mm))
```

The table below shows the min, 1st quartile, median, mean, 3rd quartile, max value, and number of NA's of the variable *bill_depth_mm*
```{r, echo=FALSE}
summary(pull(penguins,bill_depth_mm))
```

The table below shows the min, 1st quartile, median, mean, 3rd quartile, max value, and number of NA's of the variable *flipper_length_mm*
```{r, echo=FALSE}
summary(pull(penguins,flipper_length_mm))
```

The table below shows the min, 1st quartile, median, mean, 3rd quartile, max value, and number of NA's of the variable *body_mass_g*
```{r, echo=FALSE}
summary(pull(penguins,body_mass_g))
```

There are `r nrow(penguins)` rows and `r ncol(penguins)` columns.

The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = T)`

**Scatter plot of flipper_length_mm (y) vs bill_length_mm (x)**

```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color=species)) + geom_point()
```

Save the scatter plot as "hw1_scatterplot"
```{r}
ggsave("hw1_scatterplot.pdf")
```

